Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete fields complexity subsection

From the

>>>>

The Figure shows a very similar correlation to the one for comments complexity. A correlational analysis revealed 
a weak positive relationship with $r = 0.178$ and $p < 0.01$. This implies both that our results are statistically 
significant and also that as number of words in summary and description increase, the Time-To-Close increases, thus 
the quality of the ticket decreases.

This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
Zimmermann et. al \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
reduce the effort invested by the developers.

Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
in some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
is that the information that could all be put in description should be split across these fields: 
\begin{itemize}
  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
  created exclusively for them; 
  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
  Jira system field called \"Story Points\";
  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
  document) and attach it separately so that they keep the description clean and easy to follow.
\end{itemize}

A solution for this issue could be the freedom of easily selecting the total number of words allowed for summary and 
description. Even though this is possible with Jira, the process of configuring it is not trivial, thus many 
administrators do not perform this step. An even better approach would be to have a tool automatically generating 
word limits based on, for example, the experience of the reporter - if he/she has significant knowledge regarding 
the project, they should be allowed to include lengthier summaries or descriptions mainly because they are more inclined 
to know that without a very good reason, following this approach is not the most optimal way.

Another simple and straightforward solution can be the simple addition of hints below or above the text boxes for summary 
and description where administrators can write succint messages adivising reporters to not write verbose paragraphs 
unless they really have a very good reason to do so.
